|

### 2019-07-17 inst/manuscript/manuscript.Rmd
Adjust Figure 3 and 5

```{r figure1Data, include=FALSE, cache=TRUE}
# construct data.frame with nta experiment info
nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
                                  "Biofilm_4", "Biofilm_5", 
                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
                           protein_conc = c(0.192, 0.282, 0.287, 
                                            0.424, 0.716, 0.584, 
                                            0.204, 0.198, 0.297, 0.193, 0.416, 
                                            0.437, 0.360, 0.447), 
                           stringsAsFactors = FALSE)

@@

f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73:75,77), f3_pal) + 
  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)

>>>>

```{r figure1Data, include=FALSE}
# construct data.frame with nta experiment info
nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
                                  "Biofilm_4", "Biofilm_5", 
                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
                           protein_conc = c(0.192, 0.282, 0.287, 
                                            0.424, 0.716, 0.584, 
                                            0.204, 0.198, 0.297, 0.193, 0.416, 
                                            0.437, 0.360, 0.447), 
                           stringsAsFactors = FALSE)

@@

f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73,75,77,87), f3_pal) + 
  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)
